%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Problem statement
\begin{statement}[
  problempoints=110,
  timelimit=1 second,
  memorylimit=512 MiB,
]{Zapina}

There is a total of $N$ young programmers which are preparing for the second
part of competitive season during a winter camp in \sout {Krapina} Zagreb.
Mr. Malnar, a big promoter of order, discipline and hard work, told the
programmers to form a line and gave each of them a certain number (possibly zero)
tasks. He gave away a total of \textbf{N different} tasks and he knows that the
$i$-th programmer in line will be happy if they got exactly $i$ tasks.

In how many different ways could Mr. Malnar give out the tasks in such a way
that \textbf{at least one} programmer was happy? Two ways of giving out the
tasks are considered different if there exists a programmer and a task such that
in one way that programmer received that task while in the other one they
didn't.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Input
\subsection*{Input}
The first line contains an integer $N$ $(1 \le N \le 350)$ from task
description.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Output
\subsection*{Output}
Output the sought number of ways modulo $10^9+7$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Scoring
 \subsection*{Scoring}
{\renewcommand{\arraystretch}{1.4}
  \setlength{\tabcolsep}{6pt}
  \begin{tabular}{ccl}
 Subtask & Score & Constraints \\ \midrule
  1 & 22 & $1 \le N \le 7$ \\
  2 & 33 & $1 \le N \le 20$ \\
  3 & 55 & No additional constraints.
\end{tabular}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Examples
\subsection*{Examples}
\begin{tabularx}{\textwidth}{X'X'X}
\sampleinputs{test/zapina.dummy.in.1}{test/zapina.dummy.out.1} &
\sampleinputs{test/zapina.dummy.in.2}{test/zapina.dummy.out.2} &
\sampleinputs{test/zapina.dummy.in.3}{test/zapina.dummy.out.3}
\end{tabularx}

\textbf{Clarification of the second example:}

Ways of giving out the tasks in which at least one programmer is
happy are:
\begin{enumerate}
  \item First task to first programmer, second task to the second one.
  \item Second task to the first programmer, first task to the second one.
  \item Both tasks to the second programmer.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% We're done
\end{statement}

%%% Local Variables:
%%% mode: latex
%%% mode: flyspell
%%% ispell-local-dictionary: "croatian"
%%% TeX-master: "../hio.tex"
%%% End:
