%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Problem statement
\begin{statement}[
  problempoints=110,
  timelimit=? seconds,
  memorylimit=512 MiB,
]{Matching}

You are given $N$, where $N$ is even, points on a plane that have integer
coordinates. For each integer $a$, there are at most two points with coordinates
$(a, x)$. Analogously, for each integer $b$, there are at most two points
with coordinates $(x, b)$.

You are able to draw horizontal or vertical line segments between pairs of given
points. Is it possible to draw $\frac{N}{2}$ lines such that each of the
given points is an endpoint of exactly one line segment and that no two line
segments intersect?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Input
\subsection*{Input}
The first line contains an even integer $N$ $(2 \le N \le 100\ 000)$ from
the task description.

The $i$-th of the next $N$ lines contains two integers $X_i$, $Y_i$
$(1 \le X_i, Y_i \le 100\ 000)$, coordinates of the $i$-th point.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Output
\subsection*{Output}
If it is not possible to draw the line segments as explained in the task
statement, you should output \texttt{"NE"} (NO in Croatian) in a single line.

Otherwise, you should output \texttt{"DA"} (YES in Croatian) in the first
line. In each of the next $\frac{N}{2}$ lines you should output two
space-separated integers $i$ and $j$ $(1 \le i, j \le N)$, which represent
indices of the points that are connected with a drawn line segment.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Scoring
 \subsection*{Scoring}
{\renewcommand{\arraystretch}{1.4}
  \setlength{\tabcolsep}{6pt}
  \begin{tabular}{ccl}
 Subtask & Score & Constraints \\ \midrule
    1 & 5 &   \makecell[l]{$2 \le N \le 20$, for each integer $a$, there is an even
              number of points with coordinates $(a, x)$ \\ and an even number
              of points with coordinates
              $(x, a)$. } \\
  2 & 6 & $2 \le N \le 20$ \\
  3 & 7 & $2 \le N \le 40$ \\
  4 & 40 & $2 \le N \le 2000$ \\
  5 & 52 & No additional constraints.
\end{tabular}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Examples
\subsection*{Examples}
\begin{tabularx}{\textwidth}{X'X'X}
\sampleinputs{test/matching.dummy.in.1}{test/matching.dummy.out.1} &
\sampleinputs{test/matching.dummy.in.2}{test/matching.dummy.out.2} &
\sampleinputs{test/matching.dummy.in.3}{test/matching.dummy.out.3}
\end{tabularx}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% We're done
\end{statement}

%%% Local Variables:
%%% mode: latex
%%% mode: flyspell
%%% ispell-local-dictionary: "croatian"
%%% TeX-master: "../hio.tex"
%%% End:
