%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Problem statement
\begin{statement}[
  problempoints=110,
  timelimit=1 second,
  memorylimit=512 MiB,
]{Putovanje}

Little Fabijan loves bars and travels. He wishes to drink \sout{beer} coffee in
each of the $N$ towns in his country conveniently numbered from $1$ to $N$.
The towns are connected via $(N - 1)$ bidirectional roads such that each town
is reachable from any other town by traversing some of the roads. Fabijan
decided to drink coffee in every town in order from town number $1$ to town
number $N$.  Therefore, he starts from town number $1$ (where he drinks his
first coffee) and travels to town number $2$ for his next cup of coffee.
During that travel he might pass through a number of different towns but he
won't make a coffee stop in those towns. After drinking coffee in town $2$,
he will proceed to travel to town $3$, and so on until he finally reaches
town $N$ where he will drink his last coffee.

In order to traverse a certain road, he needs to have a valid ticket. The $i$-th
road can be traversed if you have either a single-pass ticket which costs $C_{i1}$
euros or a multi-pass ticket which costs $C_{i2}$ euros. For each road, Fabijan can
decide to buy a single-pass ticket each time he needs to traverse that road or
he might opt to buy a multi-pass ticket once.

Write a program that computes the smallest number of euros Fabijan needs to spend
on tickets in order to successfully complete his travels.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Input
\subsection*{Input}
The first line contains an integer $N$ $(2 \le N \le 200\ 000)$ from task
description.

In $i$-th of the next $(N - 1)$ lines there are four integers $A_i$, $B_i$,
$C_{i1}$, $C_{i2}$ $(1 \le A_i, B_i \le N, 1 \le C_{i1} \le C_{i2} \le 100\
000)$ which represent that towns $A_i$ and $B_i$ are connected with
a road with ticket prices $C_{i1}$ and $C_{i2}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Output
\subsection*{Output}
In a single line output the smallest cost of travel.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Scoring
 \subsection*{Scoring}
{\renewcommand{\arraystretch}{1.4}
  \setlength{\tabcolsep}{6pt}
  \begin{tabular}{ccl}
 Subtask & Score & Constraints \\ \midrule
  1 & 20 & $2 \le N \le 2000$ \\
  2 & 25 & Each town will be directly connected with at most two other towns. \\
  3 & 65 & No additional constraints.
\end{tabular}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Examples
\subsection*{Examples}
\begin{tabularx}{\textwidth}{X'X'X}
\sampleinputs{test/putovanje.dummy.in.1}{test/putovanje.dummy.out.1} &
\sampleinputs{test/putovanje.dummy.in.2}{test/putovanje.dummy.out.2} &
\sampleinputs{test/putovanje.dummy.in.3}{test/putovanje.dummy.out.3}
\end{tabularx}

\clearpage

\textbf{Clarification of the first example:}

Fabijan first travels from town $1$ to town $2$ and it is optimal for
him to buy a multi-pass ticket ($5$ euros) for the road which connects them.
Then he travels from town $2$ to town $3$ via town $1$. He already has a
multi-pass ticket that takes him from $2$ to $1$ and he buys a single-pass
ticket from town $1$ to town $3$ ($2$ euros). On his travels from town $3$ to
town $4$ he buys another single-pass ticket that takes him from town $3$ back
to town $2$ ($2$ euros) and after that buys a single-pass ticket that takes him from town $2$
to town $4$ ($1$ euro). In total, he spent $5+2+2+1=10$ euros.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% We're done
\end{statement}

%%% Local Variables:
%%% mode: latex
%%% mode: flyspell
%%% ispell-local-dictionary: "croatian"
%%% TeX-master: "../hio.tex"
%%% End:
