\documentclass[a4paper]{article}
\usepackage{zadaci}
\usepackage{wrapfig}
\usepackage{url}
\usepackage{tikz}
\usepackage{amsmath}
\usepackage[normalem]{ulem}
\usetikzlibrary{angles,quotes}
\contestname{Croatian Open Competition in Informatics\\Round 5, February 8\textsuperscript{th} 2020}
\markright{\textbf{\textsf{Editorial}}}

\usepackage{hyperref}
\hypersetup{
colorlinks=true,
linkcolor=blue,
filecolor=magenta,
urlcolor=cyan,
}

\begin{document}

\section*{Editorial}

Tasks, test data and solutions were prepared by: Nikola Dmitrović, Karlo
Franić, Gabrijel Jambrošić, Marin Kišić, Daniel Paleka, Ivan Paljak and Paula
Vidas. Implementation examples are given in attached source code files.

\subsection*{Task: Emacs}
\textsf{Suggested by: Paula Vidas}\\
\textsf{Necessary skills: implementation}

The number of rectangles in the image is equal to the number of upper-left
corners of rectangles in the image. Cell $(i, j)$ is an upper-left corner of
some rectangle if that cell contains the character \texttt{'*'} while cells $(i
- 1, j)$ and $(i, j - 1)$ (if they exist) contain the character \texttt{'.'}.

Alternatively, we can use BFS to find the number of connected components in four
general directions which contain the character \texttt{'*'}.

\subsection*{Task: Političari}
\textsf{Suggested by: Ivan Paljak}\\
\textsf{Necessary skills: cycle detection}

It was possible to score $50\%$ ($35$) of total points on this task
simply by implementing what was described in the task statement. In other
words, you should have correctly implemented the rules by which politicians
blame each other until we reach the $K$-th show. The time complexity of this
solution is $\mathcal{O}(K)$, and the implementation details can be seen
in \texttt{politicari\_brute.cpp}.

To score all points on this task it was necessary to observe that the blaming
process is cyclical. Since the next guest on a talk show solely depends on the
previous guest and the person who blamed the previous guest, we can conclude
that there are at most $\mathcal{O}(N^2)$ different shows (states). We consider
two shows to be the same if they have the same guest that was blamed by the
same politician in the previous show. Otherwise, the shows are considered
different.

Since the total number of different shows is considerably less than the maximum
episode in which we are interested in, we can simulate the process until we
reach the show we have seen before (already visited state). At that moment,
assuming that we keep track of some key items that have happened, we can use
the power of math to calculate who will be the guest of the $K$-th show.

Let's assume we have realized that the $i$-th show will be the same as a
(some prior) $j$-th show. In that case, we have just entered a cycle of
length $(i-j)$ and can conclude that the guest which appeared in $(j + ((K -
j) \% (i - j)))$-th show will also appear in the $K$-th show. Here, we
use the $\%$ character to denote the modulo operator.

Time complexity of described solution is $\mathcal{O}(N^2)$.

\clearpage

\subsection*{Task: Matching}
\textsf{Suggested by: Paula Vidas and Daniel Paleka}\\
\textsf{Necessary skills: segment tree}

If we connect the points that share one coordinate, the points will be
divided into \textit{cycles} and \textit{paths}. With paths it is clear which
points should be connected with line segments. If there is a path with an odd
number of points, we immediately conclude that the answer is \texttt{"NE"}. For
cycles we must determine whether we will draw all horizontal or all vertical
lines (in the rest of the editorial we call this \textit{orientation}).

There are at most $\frac{N}{4}$ cycles, so in a subtask where $(N \le 40)$
we can try all $2^{\text{broj ciklusa}}$ possible cycle orientations and check
if there is one where line segments don't intersect.

The main idea is as follows: at the beginning the paths determine some line
segments that must be drawn. These line segments determine the orientations
of those cycles that they intersect, which determine the orientations of some
other cycles, etc. If at some point during this process we draw a line segment
that intersects some line segment that is already drawn or we conclude that
both cycle orientations are invalid, then the answer is \texttt{"NE"}.

For a subtask where $N \leq 2000$, we can do that in $\mathcal{O}(N^2)$:

First, we find all paths and cycles and place all line segments from paths into
a \textit{FIFO queue} of the lines that need to be drawn. While the queue is not
empty, we pop a line segment from it and check whether it intersects any of the
previously drawn line segments (then the answer is \texttt{"NE"}). Then we
traverse over not-yet-oriented cycles and orient those cycles which intersect
with the line segment we are about to draw (orientation of the cycle needs to
be different than the orientation of the line segment). In the end we might have
some leftover cycles which we can orient in the same orientation (doesn't matter
which one).

For the final subtask where $N \le 10^5$, we need to check those line segment
intersections more efficiently. We will use a segment tree to devise a data
structure which supports the following operations:

\begin{itemize}
  \item add a line segment $(x_1, y)$ -- $(x_2, y)$
  \item remove a previously added line segment $(x_1, y)$ -- $(x_2, y)$
  \item determine for some $x$ and $y_1$ what is the smallest $y_2 \ge y_1$ such that
    there exists a line segment with $y$ coordinate equal to $y_2$ which contains
    the point $(x, y_2)$ (or determine that no such $y_2$ exists)
\end{itemize}

In each node of the segment tree we will store a set of all $y$ coordinates
whose $x$ coordinates are in an interval for which that node is responsible.
The first two operations boil down to standard addition/deletion of $y$ to
corresponding nodes. To answer the third operation, we will find such $y_2$ for
each node responsible for $x$ (e.g. by using \texttt{lower\_bound} in \texttt{std::set}) and
return minimal such value. The complexity of all three operations is
$\mathcal{O}(\log^2 N)$. For implementation details, check the official solution.

Line segment which intersects the line segment $(x, y_1)$ -- $(x, y_2)$ exists if
the answer to the third query for $x$ and $y_1$ is less than or equal to $y_2$.

We will use two such data structures -- one for horizontal and one for vertical
line segments -- in which we will store the line segments of not-yet-oriented
cycles and two additional data structures to store already drawn line segments.
We leave out the rest of the details as an exercise to the reader.

\clearpage

\subsection*{Task: Putovanje}
\textsf{Suggested by: Gabrijel Jambrošić and Marin Kišić}\\
\textsf{Necessary skills: lca, small-to-large}

Note that we really care about the number of times we need to traverse
each of the roads. Once we know that, it is pretty easy to decide whether
we will buy multiple single-pass tickets or a single multi-pass ticket.

In the first subtask, it was enough to use an algorithm like BFS or DFS to
find a path between $X$ and $X+1$ while increasing the counter of traversals
for each edge.

In the second subtask our tree is actually a chain. Let's think about that
chain as an array. Let's also keep around another array called \texttt{dp}.
Now, for every pair $X$ and $X+1$ we can increase \texttt{dp[min(pos[X], pos[X+1])]}
by $1$ and decrease \texttt{dp[max(pos[X], pos[X+1])]} by $1$ where \texttt{pos[x]}
denotes the position of node $x$ in our chain. After we have done this for all
neighbouring pairs, we can go over the \texttt{dp} array and add its elements
into some variable \texttt{cnt}. Note that in each moment of this traversal that
variable holds the number of times we have traversed the corresponding edge
in a chain.

To score all points we will slightly modify this algorithm to make it work
on a tree. Let's root the tree in an arbitrary node. Let $L$ be the lowest
common ancestor of $X$ and $(X+1)$. Let's now increase \texttt{dp[X]} by
$1$, increase \texttt{dp[X+1]} by 1 and decrease \texttt{dp[L]} by $2$.
Now we can simply find out the number of traversals of each road by calculating
the sum of \texttt{dp} values in a subtree of that road.

This solution is implemented in \texttt{putovanje\_lca.cpp}.

There is an alternative solution of the same time complexity which uses the
so-called \textit{small-to-large} trick. That solution is implemented in
\texttt{putovanje\_stl.cpp}. You can read about a very similar idea
on this \href{https://codeforces.com/blog/entry/72017#comment-563190}{link}.


\subsection*{Task: Zapina}
\textsf{Suggested by: Marin Kišić and Paula Vidas}\\
\textsf{Necessary skills: dynamic programming, counting}

The first subtask can be solved by simply checking if there is at least one
happy programmer for each possible assignment of tasks. There are $N^N$
possible task assignments in total.

The second subtask can be solved using the inclusion-exclusion principle.
If with $a(S)$, where $S \subseteq \{1, 2, \ldots, N\}$, denotes the number
of task assignments in which all programmers from set $S$ are happy, then the
number of good assignments is equal to

$$\sum_{S \subseteq \{1, 2, \ldots, N\}}{(-1)^{|S| + 1} a(S)}.$$

Let $S = \{s_1, s_2, \ldots, s_k\}$. If $s_1 + s_2 + \cdots + s_k > N$
then obviously $a(S) = 0$. Otherwise, it holds

$$a(S) = \binom{N}{s_1} \binom{N - s_1}{s_2} \cdots \binom{N - (s_1 + s_2 +
\cdots s_{k-1})}{s_k} (N - k)^{N - (s_1 + s_2 + \cdots + s_k)}.$$

Binomial coefficients can be precomputed using the well-known relation
$\binom{n}{k} = \binom{n - 1}{k - 1} + \binom{n - 1}{k}$ in time complexity
$\mathcal{O}(N^2)$.

The total time complexity is $\mathcal{O}(N 2^N)$.

Finally, the third subtask can be solved using dynamic programming. Let $dp(n, k)$
be the number of assignments of $k$ tasks to $n$ programmers among which there is
at least one happy programmer. There are two possibilities -- we can give the $n$-th
programmer exactly $n$ tasks (and make him happy), or we won't. In the first case,
if $k \geq n$, the number of ways equals

$$\binom{k}{n} (n - 1)^{(k - n)},$$

and in the other it equals

$$\sum_{0 \leq i \leq k, i \neq n}{\binom{k}{i} dp(n - 1, k - i)}.$$

The total time complexity is $\mathcal{O}(N^3)$.

\end{document}
%%% Local Variables:
%%% mode: latex
%%% mode: flyspell
%%% ispell-local-dictionary: "croatian"
%%% End:
